\documentclass[12pt,letterpaper]{article}
\usepackage{graphicx,textcomp}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{fullpage}
\usepackage{color}
\usepackage[reqno]{amsmath}
\usepackage{amsthm}
\usepackage{fancyvrb}
\usepackage{amssymb,enumerate}
\usepackage[all]{xy}
\usepackage{endnotes}
\usepackage{lscape}
\newtheorem{com}{Comment}
\usepackage{float}
\usepackage{hyperref}
\newtheorem{lem} {Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{obs}{Observation}
\usepackage[compact]{titlesec}
\usepackage{dcolumn}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{multirow}
\usepackage{xcolor}
\newcolumntype{.}{D{.}{.}{-1}}
\newcolumntype{d}[1]{D{.}{.}{#1}}
\definecolor{light-gray}{gray}{0.65}
\usepackage{url}
\usepackage{listings}
\usepackage{color}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
	backgroundcolor=\color{backcolour},   
	commentstyle=\color{codegreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{codegray},
	stringstyle=\color{codepurple},
	basicstyle=\footnotesize,
	breakatwhitespace=false,         
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=true,                 
	numbers=left,                    
	numbersep=5pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=2
}
\lstset{style=mystyle}
\newcommand{\Sref}[1]{Section~\ref{#1}}
\newtheorem{hyp}{Hypothesis}


\title{Problem Set 4}
\date{Zexi Wang}
\author{Applied Stats/Quant Methods 1}


\begin{document}
	\maketitle
	\section*{Instructions}
	\begin{itemize}
		\item Please show your work! You may lose points by simply writing in the answer. If the problem requires you to execute commands in \texttt{R}, please include the code you used to get your answers. Please also include the \texttt{.R} file that contains your code. If you are not sure if work needs to be shown for a particular problem, please ask.
		\item Your homework should be submitted electronically on GitHub.
		\item This problem set is due before 23:59 on Monday November 18, 2024. No late assignments will be accepted.
	\end{itemize}



	\vspace{.5cm}
\section*{Question 1: Economics}
\vspace{.25cm}
\noindent 	
In this question, use the \texttt{prestige} dataset in the \texttt{car} library. First, run the following commands:

\begin{verbatim}
install.packages(car)
library(car)
data(Prestige)
help(Prestige)
\end{verbatim} 


\noindent We would like to study whether individuals with higher levels of income have more prestigious jobs. Moreover, we would like to study whether professionals have more prestigious jobs than blue and white collar workers.

\newpage
\begin{enumerate}
	
	\item [(a)]
	Create a new variable \texttt{professional} by recoding the variable \texttt{type} so that professionals are coded as $1$, and blue and white collar workers are coded as $0$ (Hint: \texttt{ifelse}).
	\lstinputlisting[language=R, firstline=34, lastline=44]{PS4_Zexi_Wang.R}
	
	\item [(b)]
	Run a linear model with \texttt{prestige} as an outcome and \texttt{income}, \texttt{professional}, and the interaction of the two as predictors (Note: this is a continuous $\times$ dummy interaction.)
	\lstinputlisting[language=R, firstline=45, lastline=49]{PS4_Zexi_Wang.R}
	\begin{footnotesize}
	\begin{verbatim}
	================================================
	Dependent variable:    
	---------------------------
	prestige          
	------------------------------------------------
	income                        0.003***          
	(0.0005)          
	
	professional1                 37.781***         
	(4.248)          
	
	income:professional1          -0.002***         
	(0.001)          
	
	Constant                      21.142***         
	(2.804)          
	
	------------------------------------------------
	Observations                     98             
	R2                              0.787           
	Adjusted R2                     0.780           
	Residual Std. Error        8.012 (df = 94)      
	F Statistic            115.878*** (df = 3; 94)  
	================================================
	Note:                *p<0.1; **p<0.05; ***p<0.01
	\end{verbatim}
	\end{footnotesize} 

	\item [(c)]
	Write the prediction equation based on the result.
	\begin{equation*}
 Prestige = 21.142 + 0.003*Income + 37.781*Professional - 0.002*Income*Professional 
    \end{equation*}

	\item [(d)]
	Interpret the coefficient for \texttt{income}.
	\begin{verbatim}
The coefficient for income in the regression model indicates the 
expected change in the prestige score for each additional dollar 
earned.For blue-collar and white-collar workers, for each additional 
dollar of income, the prestige score is expected to increase by 
0.003 on average.
	\end{verbatim}
		
	\item [(e)]
	Interpret the coefficient for \texttt{professional}.
	\begin{verbatim}
The coefficient for professional shows the expected change in prestige 
score when moving from a white-collar or blue-collar position to a 
professional role, with income at zero. A professional worker is 
expected to have a prestige score that is 37.781 points higher 
than an equally low-income white-collar or blue-collar worker.
	\end{verbatim}
	
	\item [(f)]
	What is the effect of a \$1,000 increase in income on prestige score for professional occupations? In other words, we are interested in the marginal effect of income when the variable \texttt{professional} takes the value of $1$. Calculate the change in $\hat{y}$ associated with a \$1,000 increase in income based on your answer for (c).
	\lstinputlisting[language=R, firstline=60, lastline=62]{PS4_Zexi_Wang.R}
	\begin{verbatim}
The marginal increase in prestige score is 0.8452
	\end{verbatim}
	
	\item [(g)]
	What is the effect of changing one's occupations from non-professional to professional when her income is \$6,000? We are interested in the marginal effect of professional jobs when the variable \texttt{income} takes the value of $6,000$. Calculate the change in $\hat{y}$ based on your answer for (c).
	\lstinputlisting[language=R, firstline=63, lastline=65]{PS4_Zexi_Wang.R}
	\begin{verbatim}
Changing one's occupation from a non-professional to a professional worker 
at an income of $6,000 results in an increase of 23.83 in the prestige score.
	\end{verbatim}
\end{enumerate}

\newpage

\section*{Question 2: Political Science}
\vspace{.25cm}
\noindent 	Researchers are interested in learning the effect of all of those yard signs on voting preferences.\footnote{Donald P. Green, Jonathan	S. Krasno, Alexander Coppock, Benjamin D. Farrer,	Brandon Lenoir, Joshua N. Zingher. 2016. ``The effects of lawn signs on vote outcomes: Results from four randomized field experiments.'' Electoral Studies 41: 143-150. } Working with a campaign in Fairfax County, Virginia, 131 precincts were randomly divided into a treatment and control group. In 30 precincts, signs were posted around the precinct that read, ``For Sale: Terry McAuliffe. Don't Sellout Virgina on November 5.'' \\

Below is the result of a regression with two variables and a constant.  The dependent variable is the proportion of the vote that went to McAuliff's opponent Ken Cuccinelli. The first variable indicates whether a precinct was randomly assigned to have the sign against McAuliffe posted. The second variable indicates
a precinct that was adjacent to a precinct in the treatment group (since people in those precincts might be exposed to the signs).  \\

\vspace{.5cm}
\begin{table}[!htbp]
	\centering 
	\textbf{Impact of lawn signs on vote share}\\
	\begin{tabular}{@{\extracolsep{5pt}}lccc} 
		\\[-1.8ex] 
		\hline \\[-1.8ex]
		Precinct assigned lawn signs  (n=30)  & 0.042\\
		& (0.016) \\
		Precinct adjacent to lawn signs (n=76) & 0.042 \\
		&  (0.013) \\
		Constant  & 0.302\\
		& (0.011)
		\\
		\hline \\
	\end{tabular}\\
	\footnotesize{\textit{Notes:} $R^2$=0.094, N=131}
\end{table}

\begin{enumerate}
	\item [(a)] Use the results from a linear regression to determine whether having these yard signs in a precinct affects vote share (e.g., conduct a hypothesis test with $\alpha = .05$).
	\lstinputlisting[language=R, firstline=66, lastline=75]{PS4_Zexi_Wang.R}
	\begin{verbatim}
H0:lawn yard signs do not affect vote share (effect = 0)
Ha:lawn yard signs do affect vote share

Given that the p-value of 0.0097 is less than the significance level of 0.05, 
we reject the null hypothesis, providing statistically significant evidence 
that lawn signs in a precinct do have an effect on vote share.
    \end{verbatim}
		
	\item [(b)]  Use the results to determine whether being
	next to precincts with these yard signs affects vote
	share (e.g., conduct a hypothesis test with $\alpha = .05$).
	\lstinputlisting[language=R, firstline=76, lastline=82]{PS4_Zexi_Wang.R}
	\begin{verbatim}
H0:being next to precincts with these yard signs does not affect vote share
Ha:being next to precincts with these yard signs affects vote share

Since the p-value of 0.0015 is less than the significance level of 0.05, we 
reject the null hypothesis, providing statistically significant evidence 
that precincts next to yard signs do have an effect on vote share.
    \end{verbatim}

	\item [(c)] Interpret the coefficient for the constant term substantively.

	
	\item [(d)] Evaluate the model fit for this regression.  What does this	tell us about the importance of yard signs versus other factors that are not modeled?
	
\end{enumerate}  


\end{document}
